`forestecology` package for modeling interspecies competition between trees

### 2021-01-13 etc/paper/forestecology.Rmd

1. Set the context for and purpose of the work: The scientific question/problem and the desiderata
    + fitting models for interspecific competition and assessing them using spatial crossvalidation
    + Leverage ForestGEO protocols providing standardization
1. Indicate the approach and the methods: Use tidyverse, simple features, and tidymodels packages. 
    + tidyverse: as stated in tidy tools manifesto: standadized data structures, functional programming with pipe, designed for humans
    + sf: tidyverse-friendly package that makes wrangling and visualizing spatial data much easier
    + tidymodels: given our spatial-crossvalidation, use tidymodels framework is a collection of packages for modeling and machine learning using tidyverse principles
    + Dave: hmm, I think here we might need to mention the methods we implement. Something like, the package provides functions to specific a linear, bayesian neighborhood competition model of growth, then fit the model, and compare competing models with spatiall cross validation. Or somethign like that.
1. Outline the main results: We replicate from scratch the figure in PLOSOne paper using Big Woods data, conduct similar analysis for SCBI data.
    + Code would've been way more complicated in base. 
    + We don't have to worry about how the component functions work, only that sequence/converyor belt is correct and output is correct.
    + Scientist is abstracted away from ugly programming details.
1. Identify the conclusions and wider implications:
    + New scientific conclusions from SCBI data
    + this can serve as blue print for other modeling situations.
    + Modularly switch out our bayesian lm() functions to anything you want.

>>>>

1. Set the context for and purpose of the work: The scientific question/problem and the desiderata
    + (Eventually) modularly fitting models for interspecific competition and assessing them using spatial crossvalidation
    + Leverage ForestGEO protocols providing standardization
1. Indicate the approach and the methods: Use tidyverse, simple features, and tidymodels packages. 
    + tidyverse: as stated in tidy tools manifesto: standadized data structures, functional programming with pipe, designed for humans
    + sf: tidyverse-friendly package that makes wrangling and visualizing spatial data much easier
    + tidymodels: given our spatial-crossvalidation, use tidymodels framework is a collection of packages for modeling and machine learning using tidyverse principles
    + Dave: hmm, I think here we might need to mention the methods we implement. Something like, the package provides functions to specific a linear, bayesian neighborhood competition model of growth, then fit the model, and compare competing models with spatiall cross validation. Or somethign like that.
1. Outline the main results: We replicate from scratch the figure in PLOSOne paper using Big Woods data, conduct similar analysis for SCBI data.
    + Code would've been way more complicated in base. 
    + We don't have to worry about how the component functions work, only that sequence/converyor belt is correct and output is correct.
    + Scientist is abstracted away from ugly programming details.
1. Identify the conclusions and wider implications:
    + New scientific conclusions from SCBI data
    + Modularly switch out our bayesian lm() functions to anything you want.
    + this can serve as blue print for other modeling situations.
